---
title: 'SDMA AGE Effects: Exploratory ManyBabies Habituation Project'
author: "Arya Mallik"
date: "2026-06-23"
output:
  html_document: yes
  keep_md: yes
questions_answered: "1. do older infants look less overall? 2.  do older infants habituate faster?"
description: "This Rmd contains code for conducting a single dataset meta-analysis
  looking at age effects (main, and interactions with trial).
  for many-analysts studies. I focus on RQ2: Are there individual differences in habtiuation?"
---

## Helper functions

These are helper functions to facilitate the SDMA, taken from – They include functions for classical and Bayesian SDMA, and plotting functions.

```{r setup, include = FALSE}
# helper functions 
## code changed a bit for NA values; old code: N <- median(ni) 
# Before calling NoBMA in run_mama_bayes:
run_mama_bayes <- function(yi, sei, id_team, es_type, ni=NULL){
  
  if(es_type == "Cohen's d" | es_type == "Hedges' g"){
    outcome_scale <- sqrt(2)
  } else if(es_type == "log odds ratio" | es_type == "log hazard ratio" | es_type == "log relative risk"){
    outcome_scale <- sqrt(4)
  } else if(es_type == "z cor"){
    outcome_scale <- 1
} else if(es_type == "beta"){
  if(is.null(ni)) stop("For standardized regression coefficients (beta), please provide the vector of sample sizes (ni) per team.")
  
  N <- median(ni)
  fit_scale     <- metafor::rma(yi = yi, sei = sei, method = "FE")
  outcome_scale <- fit_scale$se * sqrt(sum(length(yi) * N))
  
  # DEBUG: check N and outcome_scale
  print("DEBUG: N and outcome_scale")
  print(N)
  print(outcome_scale)
  
} else {
    stop("The effect size type (es_type) needs to be one of: 'Cohen's d', 'Hedges' g', 'log odds ratio', 'log hazard ratio', 'log relative risk', 'z cor', or 'beta'.")
  }
  
  
  n_team <- length(unique(id_team))
  team_counts <- table(id_team)
  w <- mapply(function(team) {
    rep(1 / n_team / team_counts[team], team_counts[team])
  }, names(team_counts), SIMPLIFY = FALSE)
  w <- unlist(w)[order(match(id_team, names(team_counts)))]
  
fit1 <- NoBMA(y = yi, se = sei,
              priors_effect        = prior("normal", list(mean = 0, sd = outcome_scale)),
              priors_heterogeneity = prior("normal", list(mean = 0, sd = outcome_scale/2), list(lower = 0, upper = Inf)),
              seed=2025)

sfit1 <- summary(fit1, conditional = TRUE)

# DEBUG: inspect estimates_conditional, especially tau
print("DEBUG: sfit1$estimates_conditional")
print(sfit1$estimates_conditional)

tau_est_conditional <- sfit1$estimates_conditional["tau", "Median"]

# DEBUG: check tau_est_conditional
print("DEBUG: tau_est_conditional")
print(tau_est_conditional)

fit2 <- NoBMA(y = yi, se = sqrt(sei^2 / w),
              priors_effect             = prior("normal", list(mean = 0, sd = outcome_scale)),
              priors_heterogeneity      = prior("spike",  list(location = tau_est_conditional)),
              priors_heterogeneity_null = NULL, algorithm = "ss", adapt = 10000, burnin = 10000, sample = 10000,
              seed=2025)
  # I didn't implement bridge sampling for null model with fixed heterogeneity apparently (needs to switch to product space method)
  
  # summarize results
  return(list('normal' = fit1,
              'fractional' = fit2))
}

summarize_bayes <- function(mama){
  mu    <- median(mama$fractional$RoBMA$posteriors_conditional$mu)
  se    <- sd(mama$fractional$RoBMA$posteriors_conditional$mu)
  upper <- quantile(mama$fractional$RoBMA$posteriors_conditional$mu, p=.975)
  lower <- quantile(mama$fractional$RoBMA$posteriors_conditional$mu, p=.025)
  tau   <- median(mama$normal$RoBMA$posteriors_conditional$tau)
  tau_lower <- quantile(mama$normal$RoBMA$posteriors_conditional$tau, p=.025)
  tau_upper <- quantile(mama$normal$RoBMA$posteriors_conditional$tau, p=.975)
  evidence_mu  <- mama$fractional$RoBMA$inference['Effect','inclusion_BF']
  evidence_tau <- mama$normal$RoBMA$inference$Heterogeneity$BF
  return(data.frame(
    mu = mu, se = se, mu_upper = upper, mu_lower = lower,
    tau = tau, tau_lower = tau_lower, tau_upper = tau_upper,
    evidence_mu = evidence_mu, evidence_tau = evidence_tau
  ))
}

run_mama <- function(yi, sei, id_team, es_type, ni=NULL){
  
  n_team <- length(unique(id_team))
  team_counts <- table(id_team)
  w <- mapply(function(team) {
    rep(1 / n_team / team_counts[team], team_counts[team])
  }, names(team_counts), SIMPLIFY = FALSE)
  w <- unlist(w)[order(match(id_team, names(team_counts)))]
  vi <- sei^2/w
  
  set.seed(2025)
  random1 <- try(metafor::rma(yi = yi, sei = sei, method = "REML"))
  random2 <- metafor::rma(yi = yi, vi = vi, tau2 = random1$tau2, method = "REML")
  
  confint_tau <- confint(random1)$random[2,2:3]
  bootstrapped_ci_tau <- FALSE
  
  if(confint_tau[2]==0){
    # bootstrap CI of tau
    B <- 2000
    tau_boot <- numeric(B)
    set.seed(2025)
    for(b in 1:B){
      # simulate study-level effects from fitted model
      # simulate sampling errors according to observed sei
      # predicted mean (mu_hat) can be used; here we use fitted values = overall intercept
      ystar <- rnorm(length(yi), mean = predict(random1)$pred, sd = sqrt(sei^2 + random1$tau2))
      fitb <- try(rma(yi = ystar, sei = sei, method="REML"), silent=TRUE)
      if(!inherits(fitb, "try-error")){
        tau_boot[b] <- fitb$tau2  # store tau^2 or take sqrt for tau
      } else {
        tau_boot[b] <- NA
      }
    }
    tau_boot <- na.omit(tau_boot)
    ci_tau2_boot <- quantile(tau_boot, probs = c(0.025, 0.975))
    ci_tau_boot <- sqrt(ci_tau2_boot)
    confint_tau <- ci_tau_boot
    bootstrapped_ci_tau = TRUE
  }
  
  if(es_type == "Cohen's d" | es_type == "Hedges' g"){
    outcome_scale <- sqrt(2)
  } else if(es_type == "log odds ratio" | es_type == "log hazard ratio" | es_type == "log relative risk"){
    outcome_scale <- sqrt(4)
  } else if(es_type == "z cor"){
    outcome_scale <- 1
  } else if(es_type == "beta"){
    if(is.null(ni)) stop("For standardized regression coefficients (beta), please provide the vector of sample sizes (ni) per team.")
    N <- median(ni)
    fit_scale     <- metafor::rma(yi = yi, sei = sei, method = "FE")
    outcome_scale <- fit_scale$se * sqrt(sum(length(yi) * N))
  } else {
    stop("The effect size type (es_type) needs to be one of: 'Cohen's d', 'Hedges' g', 'log odds ratio', 'log hazard ratio', 'log relative risk', 'z cor', or 'beta'.")
  }
  
  return(list('normal' = data.frame(
    mu = random1$b,
    se = random1$se,
    upper = random1$ci.ub,
    lower = random1$ci.lb,
    pval = random1$pval,
    tau2 = random1$tau2,
    Qtau2 = random1$QE,
    pval_tau2 = random1$QEp,
    ci_tau_lower = confint_tau[1],
    ci_tau_upper = confint_tau[2],
    bootstrapped_ci_tau = bootstrapped_ci_tau
  ),
  'fractional' = data.frame(
    mu = random2$b,
    se = random2$se,
    upper = random2$ci.ub,
    lower = random2$ci.lb,
    pval = random2$pval,
    tau2 = random2$tau2
  ),
  n_team = n_team,
  i2 = random1$I2
  ))
}

summarize_metafor <- function(mama){
  mu <- mama$fractional$mu
  se <- mama$fractional$se
  upper <- mama$fractional$upper
  lower <- mama$fractional$lower
  tau <- sqrt(mama$normal$tau2)
  evidence_mu <- mama$fractional$bf10
  evidence_tau <- ifelse(mama$normal$pval_tau2 < .05, "significant", "not significant")
  return(data.frame(
    mu = mu, se = se, upper = upper, lower = lower,
    tau = tau, evidence_mu = evidence_mu, evidence_tau = evidence_tau
  ))
}
# plotting functions
forest_mama <- function(
    x1, x2,
    slab = "Study",
    es_type = "beta",
    transform = FALSE,
    title = NULL,
    subtitle = NULL,
    xmax = NULL,
    large = FALSE,
    labels = NULL,
    digits = 2,
    x_labels = NULL,
    xmin = NULL,
    est_lab = NULL
) {
  # --- pooled effects: ONLY ADJUSTED ---
  x2a <- x2$normal
  bayes_sum <- summarize_bayes(x2)  # fractional part
  # 1 = adjusted classical, 2 = adjusted Bayesian
  est_mu  <- c(x1$fractional$mu,      bayes_sum$mu)
  lCI_mu  <- c(x1$fractional$lower,   bayes_sum$mu_lower)
  uCI_mu  <- c(x1$fractional$upper,   bayes_sum$mu_upper)

  # --- per-analysis data ---
  data <- as.data.frame(x2a[["data"]])
  slab_vec <- paste0(slab, " ", 1:nrow(data))
  data$study <- slab_vec
  data$lower <- data$y - 1.96 * data$se
  data$upper <- data$y + 1.96 * data$se

  # optional exp-transform
  if (transform) {
    data_exp <- data
    data_exp$y     <- exp(data_exp$y)
    data_exp$lower <- exp(data_exp$lower)
    data_exp$upper <- exp(data_exp$upper)

    est_mu_exp <- exp(est_mu)
    lCI_mu_exp <- exp(lCI_mu)
    uCI_mu_exp <- exp(uCI_mu)

    x_breaks <- log(x_labels)  # only used if you supply x_labels for transform case
    data_exp <- dplyr::arrange(data_exp, dplyr::desc(y))
  }

  # sort studies by effect
  data <- data[order(data$y, decreasing = TRUE), ]
  data$x <- (nrow(data) + 5):6

  # y positions: 1–2 = pooled adjusted; data$x = individual analyses
  y_at <- c(1:2, data$x)

  if (large)
    y_at <- c(c(-0.17, -0.13) * nrow(data), data$x[c(1, nrow(data))])

  # y labels (left axis)
  y_labels <- c("Adjusted Classical", "Adjusted Bayesian", data$study)

  # y labels (right axis: estimates with CI)
  y_labels2 <- paste0(
    format(round(c(est_mu, data$y), digits), nsmall = 2),
    " [",
    format(round(c(lCI_mu, data$lower), digits), nsmall = 2),
    ", ",
    format(round(c(uCI_mu, data$upper), digits), nsmall = 2),
    "]"
  )

  if (transform) {
    y_labels2 <- paste0(
      format(round(c(est_mu_exp, data_exp$y), digits), nsmall = 2),
      " [",
      format(round(c(lCI_mu_exp, data_exp$lower), digits), nsmall = 2),
      ", ",
      format(round(c(uCI_mu_exp, data_exp$upper), digits), nsmall = 2),
      "]"
    )
  }

  if (large) {
    y_labels  <- c("Adjusted Classical", "Adjusted Bayesian", data$study[c(1, nrow(data))])
    y_labels2 <- c(
      paste0(
        format(round(est_mu, digits), nsmall = 2),
        " [",
        format(round(lCI_mu, digits), nsmall = 2),
        ", ",
        format(round(uCI_mu, digits), nsmall = 2),
        "]"
      ),
      "",
      est_lab
    )
    if (transform) {
      y_labels2 <- c(
        paste0(
          format(round(est_mu_exp, digits), nsmall = 2),
          " [",
          format(round(lCI_mu_exp, digits), nsmall = 2),
          ", ",
          format(round(uCI_mu_exp, digits), nsmall = 2),
          "]"
        ),
        "",
        est_lab
      )
    }
  }

  # y limits
  ylim <- c((y_at[1] - 1), max(data$x) + 1)
  if (large)
    ylim <- c((y_at[1] - 0.008 * nrow(data)), max(data$x) + 1)

  # x label
  xlab <- es_type
  if (es_type == "beta")
    xlab <- expression("Standardized " * beta)

  # --- x scale: always include 0 to avoid geom_line() warning ---
  if (!transform) {
    x_breaks <- pretty(range(c(data$lower, data$upper, lCI_mu, uCI_mu, 0)))
    x_labels <- x_breaks
  }
  xlim <- range(x_breaks)

  # add descriptive labels to the extreme ticks
  if (!is.null(labels)) {
    x_labels <- c(
      paste0(x_labels[1], "\n", labels[1]),
      x_labels[2:(length(x_labels) - 1)],
      paste0(x_labels[length(x_labels)], "\n", labels[2])
    )
  }

  alpha <- ifelse(large, 0.1, 1)
  size  <- ifelse(large, 0.8, 1)

  # polygon coordinates for the two pooled effects (diamonds)
  # 1: Adjusted Classical, 2: Adjusted Bayesian
  y_comb <- c(1, 1.25, 1, 0.75,
              2, 2.25, 2, 1.75)
  if (large) {
    y_comb <- as.vector(
      sapply(
        y_at[1:2],
        function(y) c(y, y + 0.007 * nrow(data), y, y - 0.007 * nrow(data))
      )
    )
  }

  df_polys <- data.frame(
    x     = as.vector(rbind(lCI_mu, est_mu, uCI_mu, est_mu)),
    y     = y_comb,
    group = rep(1:2, each = 4)
  )

  # --- truncation flags for xmin/xmax ---
  data$flag_upper <- FALSE
  data$flag_lower <- FALSE

  if (!is.null(xmax)) {
    data$flag_upper <- data$upper > xmax
    data$upper[data$flag_upper] <- xmax
  }
  if (!is.null(xmin)) {
    data$flag_lower <- data$lower < xmin
    data$lower[data$flag_lower] <- xmin
  }

  data_regular    <- subset(data, !flag_upper & !flag_lower)
  data_right_only <- subset(data, flag_upper & !flag_lower)
  data_left_only  <- subset(data, flag_lower & !flag_upper)
  data_both_sides <- subset(data, flag_upper & flag_lower)

  # --- build plot ---
  plot <- ggplot2::ggplot()

  # ordinary error bars
  plot <- plot +
    ggplot2::geom_errorbarh(
      data = data_regular,
      mapping = ggplot2::aes(xmin = lower, xmax = upper, y = x),
      color = "black", alpha = alpha, height = 0.25
    )

  # truncated right
  if (nrow(data_right_only) > 0) {
    plot <- plot +
      ggplot2::geom_segment(
        data = data_right_only,
        mapping = ggplot2::aes(x = lower, xend = xmax, y = x, yend = x),
        arrow = grid::arrow(length = grid::unit(0.2, "cm"), type = "open"),
        color = "black", alpha = alpha
      ) +
      ggplot2::geom_segment(
        data = data_right_only,
        mapping = ggplot2::aes(x = lower, xend = lower, y = x - 0.1, yend = x + 0.1),
        color = "black", alpha = alpha
      )
  }

  # truncated left
  if (nrow(data_left_only) > 0) {
    plot <- plot +
      ggplot2::geom_segment(
        data = data_left_only,
        mapping = ggplot2::aes(x = xmin, xend = upper, y = x, yend = x),
        arrow = grid::arrow(length = grid::unit(0.2, "cm"), type = "open", ends = "first"),
        color = "black", alpha = alpha
      ) +
      ggplot2::geom_segment(
        data = data_left_only,
        mapping = ggplot2::aes(x = upper, xend = upper, y = x - 0.1, yend = x + 0.1),
        color = "black", alpha = alpha
      )
  }

  # truncated both sides
  if (nrow(data_both_sides) > 0) {
    plot <- plot +
      ggplot2::geom_segment(
        data = data_both_sides,
        mapping = ggplot2::aes(x = lower, xend = upper, y = x, yend = x),
        arrow = grid::arrow(length = grid::unit(0.2, "cm"), type = "open", ends = "both"),
        color = "black", alpha = alpha
      )
  }

  # study points
  plot <- plot +
    ggplot2::geom_point(
      mapping = ggplot2::aes(x = data$y, y = data$x),
      shape = 15, size = size
    )

  # pooled diamonds
  plot <- plot +
    ggplot2::geom_polygon(
      data = df_polys,
      mapping = ggplot2::aes(x = x, y = y, group = group),
      fill = "black"
    )

  # vertical line at 0 (now always inside xlim because we included 0 above)
  plot <- plot +
    ggplot2::geom_line(
      mapping = ggplot2::aes(x = c(0, 0), y = ylim),
      linetype = "dotted"
    )

  # axes
  plot <- plot +
    ggplot2::theme_classic() +
    ggplot2::scale_y_continuous(
      name  = "",
      breaks = y_at,
      labels = y_labels,
      limits = ylim,
      sec.axis = ggplot2::sec_axis(
        ~.,
        breaks = y_at,
        labels = y_labels2
      )
    ) +
    ggplot2::scale_x_continuous(
      name   = xlab,
      breaks = x_breaks,
      labels = x_labels,
      limits = xlim
    ) +
    ggplot2::theme(
      axis.title.y      = ggplot2::element_blank(),
      axis.line.y       = ggplot2::element_blank(),
      axis.ticks.y      = ggplot2::element_blank(),
      axis.line.x       = ggplot2::element_line(
        arrow = grid::arrow(length = grid::unit(0.2, "cm"), ends = "both")
      ),
      axis.ticks.x      = ggplot2::element_line(linewidth = 0.5),
      axis.text.y       = ggplot2::element_text(hjust = 0, color = "black"),
      axis.text.y.right = ggtext::element_markdown(hjust = 0.5, color = "black")
    )

  if (large)
    plot <- plot + base_breaks_y(c(1, nrow(data)))

  p <- plot
  if (!large) {
    p <- cowplot::ggdraw(plot) +
      cowplot::draw_label(
        est_lab,
        x = 0.96, y = 0.96,
        angle = 0, hjust = 1, vjust = 1,
        size = 9, fontface = "bold"
      )
  }
  return(p)
}
```

## Single dataset meta-analysis: classical and Bayesian

Loading relevant packages and helper functions

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
library("papaja")
library("ggplot2")
library("gridExtra")
library("dplyr")
library("metafor")
library("parallel")
library("RoBMA")
library("ggtext")
library("cowplot")

# source("helper_functions.R")
# Pretty plots
library(ggthemes)
theme_set(
  theme_few(
    base_family = "sans",
    base_size = 12 
  ) +
    theme(panel.border = element_rect(colour="white"),
          axis.line.x = element_line(color="black"))
)

```

**SDMA for main effect the predictor variable "age" (operationalised as "age_days" centered to mean)**

Loading the dataset, containing coefficients and effect sizes from eight teams

```{r load-data}
# loading data for Q1. age main effect: do older infants habituate faster?
dat <- read.csv("C:/Arya/UvA/Thesis/dataset & analyses/sdma age main.csv")

# some inspection to check for NAs
colSums(is.na(dat))
which(is.na(dat$number))

str(dat$number)
class(dat$number) # number is a originally a character, so this kept throwing an error 

# ensure none of the big numbers in dat are separated by commas!!! 

# SEs range seems very large (i.e., ratio of largest to smallest sampling variance extremely large) so it is possible that some effects are extremely precise (tiny SE) and others very imprecise (large SE). checking for this
range(dat$se)
range(dat$se^2)
max(dat$se^2) / min(dat$se^2)

# See the most and least precise teams
dat[order(dat$se)[1:5], ]      # smallest SE
dat[order(dat$se, decreasing = TRUE)[1:5], ]  # largest SE
```

```{r run-analyses, cache=TRUE}
# run frequentist analyses (with metafor)
mama <- run_mama(yi = dat$y,     sei = dat$se,     id_team = dat$team, es_type="beta", ni=dat$number)

# run bayesian analyses (with RoBMA)
mama_bayes <- run_mama_bayes(yi = dat$y,     sei = dat$se,     id_team = dat$team, es_type="beta", ni=dat$number)
```

```{r ex3_freq}
# estimates from metafor
mama$fractional$mu
mama$fractional$lower
mama$fractional$upper
mama$fractional$pval

# heterogeneity
sqrt(mama$normal$tau2)
mama$normal$pval_tau2

# results with labels 
results <- c(
  pooled_effect_size          = mama$fractional$mu,
  lower_CI       = mama$fractional$lower,
  upper_CI      = mama$fractional$upper,
  p_value        = mama$fractional$pval,
  between_analysts_heterogeneity         = sqrt(mama$normal$tau2),
  pval_tau2   = mama$normal$pval_tau2
)

print(results)

results_df <- data.frame(
  parameter = c("pooled effect size", "lower CI", "upper CI", "p value", "between analysts heterogeneity", "pval_tau2"),
  value     = c(
    mama$fractional$mu,
    mama$fractional$lower,
    mama$fractional$upper,
    mama$fractional$pval,
    sqrt(mama$normal$tau2),
    mama$normal$pval_tau2
  )
)

options(scipen = 999)   # no scientific notation
print(results_df)

# Bayesian
median(dat$y)
range(dat$y)

# results bayesian
# > median(dat$y)
# [1] -0.1021053
# > range(dat$y)
# [1] -0.1382400 -0.0312359

# summarize_metafor(mama)
summarize_bayes(mama_bayes)

# results documented
# parameter                                            value
# 1             pooled effect size -0.092264710799520976980403474954073317348957062
# 2                       lower CI -0.125040836620459949735106874868506565690040588
# 3                       upper CI -0.059488584978581990347912267225183313712477684
# 4                        p value  0.000000034425997384137940757545259806704507355
# 5 between analysts heterogeneity  0.036828189794632648634831184608628973364830017
# 6                      pval_tau2  0.000000000000000000000000000000000000007900096

```

```{r ex_prep}
median(dat$y)
range(dat$y)
#summarize_metafor(mama4)
summarize_bayes(mama_bayes)
# plot(mama_bayes$fractional,parameter="mu")
# plot(mama_bayes$normal,parameter="tau")
mu_ci <- paste0(format(round(summarize_bayes(mama_bayes)['mu'], 2), nsmall = 2), 
                " [", format(round(summarize_bayes(mama_bayes)['mu_lower'], 2), nsmall = 2),
                ", ", format(round(summarize_bayes(mama_bayes)['mu_upper'], 2), nsmall = 2), 
                "]")
tau_ci <- paste0(format(round(summarize_bayes(mama_bayes)['tau'], 3), nsmall = 3), 
                " [", format(round(summarize_bayes(mama_bayes)['tau_lower'], 3), nsmall = 3),
                ", ", format(round(summarize_bayes(mama_bayes)['tau_upper'], 3), nsmall = 3), 
                "]")

1/mama_bayes$fractional$RoBMA$inference['Effect','inclusion_BF']
```

Forest plot

```{r dev = "png"}
ageplot1 <- forest_mama(
  x1        = mama,
  x2        = mama_bayes,
  slab      = "Analysis",
  es_type   = "beta",
  transform = FALSE,
  est_lab   = "Standardised β age [95% CI]",
  large     = FALSE,    # usually more readable
  digits    = 3,
  labels    = c(
    "Older infants show lower overall LTs",  # left side
    "Older infants show higher overall LTs"   # right side
  )
)
ggplot2::ggsave(
  "ageplot1.png",
  plot = ageplot1,
  width = 6,
  height = 5,
  units = "in",
  dpi = 300
)
```

## **SDMA for effect of age on habituation (interaction between"age" & "trial")**

```{r load-data}

# loading data for Q1. age main effect: do older infants habituate faster?
dat1 <- read.csv("C:/Arya/UvA/Thesis/dataset & analyses/sdma age x trial.csv")

# some inspection to check for NAs
colSums(is.na(dat1))
which(is.na(dat$number))

str(dat1$number)
class(dat1$number) # number is a originally a character, so this kept throwing an error 

# ensure none of the big numbers in dat are separated by commas!!! 

# SEs range seems very large (i.e., ratio of largest to smallest sampling variance extremely large) so it is possible that some effects are extremely precise (tiny SE) and others very imprecise (large SE). checking for this
range(dat1$se)
range(dat1$se^2)
max(dat1$se^2) / min(dat1$se^2)

# See the most and least precise teams
dat1[order(dat1$se)[1:5], ]      # smallest SE
dat1[order(dat1$se, decreasing = TRUE)[1:5], ]  # largest SE
```

```{r run-analyses, cache=TRUE}
# run frequentist analyses (with metafor)
mama1 <- run_mama(yi = dat1$y,     sei = dat1$se,     id_team = dat1$team, es_type="beta", ni=dat$number)

# run bayesian analyses (with RoBMA)
mama_bayes1 <- run_mama_bayes(yi = dat1$y,     sei = dat1$se,     id_team = dat1$team, es_type="beta", ni=dat1$number)

```

```{r ex3_freq}
# estimates from metafor
mama1$fractional$mu
mama1$fractional$lower
mama1$fractional$upper
mama1$fractional$pval

# heterogeneity
sqrt(mama1$normal$tau2)
mama1$normal$pval_tau2

# results with labels 
results <- c(
  pooled_effect_size          = mama1$fractional$mu,
  lower_CI       = mama1$fractional$lower,
  upper_CI      = mama1$fractional$upper,
  p_value        = mama1$fractional$pval,
  between_analysts_heterogeneity         = sqrt(mama1$normal$tau2),
  pval_tau2   = mama1$normal$pval_tau2
)

print(results)

results_df <- data.frame(
  parameter = c("pooled effect size", "lower CI", "upper CI", "p value", "between analysts heterogeneity", "pval_tau2"),
  value     = c(
    mama1$fractional$mu,
    mama1$fractional$lower,
    mama1$fractional$upper,
    mama1$fractional$pval,
    sqrt(mama1$normal$tau2),
    mama1$normal$pval_tau2
  )
)

options(scipen = 999)   # no scientific notation
print(results_df)

# documented 
#           pooled_effect_size                       lower_CI 
#                 0.00231474751                 -0.00701812713 
#                      upper_CI                        p_value 
#                 0.01164762215                  0.62688780514 
# between_analysts_heterogeneity                      pval_tau2 
#                 0.00783441034                  0.00001795154 

# Bayesian
median(dat1$y)
range(dat1$y)

# results 
# > median(dat1$y)
# [1] 0.005433362
# > range(dat1$y)
# [1] -0.007693004  0.015997525

# summarize_metafor(mama)
summarize_bayes(mama_bayes1)

```

```{r}
ageplot2 <- forest_mama(
  x1        = mama1,
  x2        = mama_bayes1,
  slab      = "Analysis",
  es_type   = "beta",
  transform = FALSE,
  est_lab   = "Standardised β age x trial [95% CI]",
  large     = FALSE,    # usually more readable
  digits    = 3,
  labels    = c(
    "older infants habituate faster",  # left side
    "older infants habituate slower"   # right side
  )
)

ggplot2::ggsave(
  "ageplot2.png",
  plot = ageplot2,
  width = 6,
  height = 5,
  units = "in",
  dpi = 300
)
```
